---
title: "Griglia di correzione — USO INTERNO"
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: false
geometry: "margin=2.5cm"
fontsize: 11pt
header-includes:
  - \usepackage{amsmath, amssymb, amsthm}
  - \usepackage{fancyhdr}
  - \usepackage{xcolor}
  - \usepackage{framed}
params:
  classe: ""
  data: ""
  argomento: ""
  durata_minuti: 60
  punteggio_totale: 30
  esercizi_json: "[]"
---

```{r setup, include=FALSE}
library(jsonlite)
library(glue)
esercizi <- jsonlite::fromJSON(params$esercizi_json, simplifyDataFrame = FALSE)
```

```{r header-setup, echo=FALSE, results='asis'}
cat(sprintf(
  "\\pagestyle{fancy}\n\\fancyhf{}\n\\fancyhead[L]{Griglia di correzione --- %s}\n\\fancyhead[R]{\\textcolor{red}{USO INTERNO}}\n\\fancyfoot[C]{\\thepage}\n\\renewcommand{\\headrulewidth}{0.4pt}\n",
  params$argomento
))
```

\begin{center}
{\large \textbf{Griglia di correzione}}\\[0.3cm]
Argomento: \textit{`r params$argomento`} \quad
Classe: \textbf{`r params$classe`} \quad
Data: `r params$data`\\[0.2cm]
Punteggio totale: \textbf{`r params$punteggio_totale` punti} \quad
Durata: `r params$durata_minuti` minuti
\end{center}

\vspace{0.5cm}

```{r soluzioni, results='asis', echo=FALSE}
for (i in seq_along(esercizi)) {
  ez <- esercizi[[i]]

  cat(glue::glue(
    "\\subsection*{{Esercizio {i} --- {ez$titolo_breve} \\hfill [{ez$punti} pt]}}\n\n"
  ))

  # Testo originale
  cat("\\begin{framed}\n\\textit{")
  cat(ez$testo)
  cat("}\n\\end{framed}\n\n")

  # Soluzione in evidenza
  cat("\\noindent\\textbf{Soluzione:} ")
  cat(ez$soluzione_finale)
  cat("\n\n")

  # Passaggi
  if (length(ez$passaggi) > 0) {
    cat("\\textbf{Svolgimento:}\n\\begin{enumerate}\n")
    for (p in ez$passaggi) {
      cat("  \\item ", p, "\n", sep = "")
    }
    cat("\\end{enumerate}\n\n")
  }

  # Suggerimento
  if (!is.null(ez$suggerimento) && nchar(ez$suggerimento) > 0) {
    cat("\\textit{\\small Suggerimento: ", ez$suggerimento, "}\n\n", sep = "")
  }

  if (i < length(esercizi)) {
    cat("\\noindent\\rule{\\textwidth}{0.4pt}\\vspace{0.5cm}\n\n")
  }
}
```

\vspace{1cm}
\begin{center}
\textcolor{red}{\textit{Documento riservato all'insegnante.}}
\end{center}
